---
title: "Lab 6"
author: "E Baker"
date: "11/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Rank based test example

Mann-Whitney U (non-parametric alternative to an unpaired 2-sample t-test).

HO (Null Hypothesis): Equal ranks (or medians)
HA (Alternative Hypothesis): Ranks are not equal (or, medians are not equal)

### Create samples

`set.seed()` to create "pseudorandom, but reproducible samples"

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size= 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size=15, replace=TRUE)
```

Take a quick look at te dirstibutions using `hist()`

```{r}
hist(gp_1)
hist(gp_2)
```

Try a t-test so we can compare the results:

```{r}
ttest<- t.test(gp_1, gp_2)

# IF these data were paired, I can just add the argument `paired = "TRUE"1 within the t.test function.
```

This p-value means that IF our samples are drawn from populations with the same mean, there is `r round(ttest$p.value,2)` probablity of finding sample means *at least as differernt* as mine by random chance. 

[A more comprehensive explaination of difference between groups... actually means, data spread, effect size]...  there is no sig difference.

### Mann Whitney U ranke based test

We  use the `wilcox.test() function to perform a two-sample rank-based test.

```{r}
mwu <- wilcox.test(gp_1, gp_2)
```

This p-vlue means that if our samples are drawn froma  pupolation with the same median, there is a 28% chance of finding sample medians at least as diferent as ours by random chance. 

No sig difference in medians via Mann-Whitney U test

Example text for reporting: "The medians of group A (M = 22.4, g) and group B( M = 31.2, g) did not difeer significantly."


# SImple linear regression

Two *continous quantitiative* variables that you are trying to understand the relationship betweeen, and you think that a linear relationship makes sense. 


Use the `penhuins` data from {palmerpenguins}, exploring flipper length (x) versus body mass (y)

```{r}
# Use View(penguins) to look at it
# Make an exploratory scatterplot of flipper length (x) vs body mass (y)

ggplot(data= penguins, aes(x= flipper_length_mm, y= body_mass_g)) +
         geom_point() +
         geom_smooth(method= "lm")

```


